Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-31 awipev-CO2.Rmd
Still on pH seafet

size_point <- 0.4 #size of data points
p <- range_month %>%
  pivot_longer(-Month, names_to = "depth", values_to = "pH_range") %>%
  ggplot() +
  geom_violin(aes(x = as.factor(Month), y = pH_range), fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(p) # plot_range_sf
#ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
```

>>>>

size_point <- 0.4 #size of data points
p <- range_month %>%
  pivot_longer(-Month, names_to = "depth", values_to = "pH_range") %>%
  ggplot() +
  #geom_violin(aes(x = as.factor(Month), y = pH_range), group = depth, fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(aes(x = as.factor(Month), y = pH_range), , group = depth, notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(p) # plot_range_sf
#ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
```
